Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-14 hscc2017/paper.tex
more comments and alignment (removed bib pages to fit page-count)

Uncertainties in $G(z)$ may appear due to: 
1. uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to explicitly encompass the effects of the uncertainty terms $\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the original model; 
2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
and 
3. errors caused by quantization (which we model later as as external noises $\nu_1$ and $\nu_2$). 
These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}. 
\end{equation}
%
%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
Notice that, due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (indeed, all other errors described in this paper are ensured to
fulfil this property in our implementation). 
We also remark that, due to its native digital implementation, 
there are no parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the controller. 
Thus $\hat{C}(z) \equiv C(z)$.

@@

A typical digital control system with a continuous plant and a discrete
controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
ADC converters introduce quantization errors (notice that each of them
may have a different FWL representation than the controller),
which are modeled as noises
$\nu_{1}(z)$ and $\nu_{2}(z)$;  
$G(s)$ is the continuous-time plant model
with parametric additive uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$ (as mentioned above);  
$R(z)$ is a given reference signal; 
$U(z)$ is the control signal; 
and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system 
%
%
%
The ADC and DAC may be abstracted by transforming the closed-loop system in
Figure~\ref{fig:sampledsystem} into the digital system in 
Figure~\ref{fig:digsystem1}, 
where 
% the parametric uncertainties are represented by~$\Delta_p \vec{G}$ and 
the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
seen as additive noise.

@@

In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
parametric uncertainties related to modeling errors  
(which are represented by~$\Delta_p \vec{G}$),  
and uncertainties introduced by quantizations in the ADC and
DAC conversions ($\nu_1$ and $\nu_2$) which are assumed to be non-deterministic. 
Recall that we discussed how the quantization noise is encompassed as an additive term, 
which means it does not enter parametrically in the transfer function. 
Instead, we later show that the system is stable given these non-deterministic noise inputs.

@@

Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
and of quantization noises in the closed-loop system.  
Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
and $Q2$ (DAC) be the source of a white noise $\nu_{2}$.  The following equation
models the system in Figure~\ref{fig:sampledsystem}, encompassing the
parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
the controller $\hat{C}(z)$:
%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z). 
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\cdot\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
\end{equation}
%
where
%
\begin{equation*}
H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}. 
\end{equation*}

@@

A discrete-time dynamical system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if bounded inputs necessarily result in bounded outputs. 
This condition holds true over an LTI model if and only if every pole of its transfer function lies inside the unit circle \cite{Astrom08}.  
Analyzing Eq.~\eqref{eq:outputfunctions}, 
the following proposition provides conditions for the BIBO stability of the system in Figure~\ref{fig:sampledsystem}, 
with regards to the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded 
(in particular, the bound on the quantization noise is given by
Assumption~\ref{whitenoise}). 
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\hat{C}(z) =\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))$ and uncertain discrete
model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
\end{equation}
\item the direct loop product $\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
\red{[wait I'm confused: the next should be a tilde!!]}
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\hat{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  We start with an a priori candidate solution
with all coefficients zero, as given below, and a precision of $I_p=16$,
$F_p=24$.  The digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ 
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$
In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

Figure~\ref{fig:step} illustrates the step responses of the closed-loop
system with the original controller represented by
Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), the
first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate
solutions provided by \tool.  The step response in Figure~\ref{fig:step0}
confirms the stability loss if we consider FWL effects.  
Figure~\ref{fig:step1} shows that the first candidate controller is able to
stabilize the closed-loop system without uncertainties, but it is rejected
during the {\sc precision} phase by \tool since this solution is not
considered to be sound.  Finally, Figure~\ref{fig:step2} shows a stable
behavior for the final (sound) solution, which presents a lower settling
time. 
\blue{[explain why 6b is continuous, but not 6c.]}

@@

\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}

\textcolor{green}{The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time}. 
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
\red{[what does this alpha-numerical code mean?]}
\textcolor{green}{CBMC (SHA-1 hash) version:} 7a6cec1dd0eb8843559591105235f1f2c4678801}

>>>>

Uncertainties in $G(z)$ may appear due to: 
1. uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to explicitly encompass the effects of the uncertainty terms $\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the original model; 
2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
and 
3. errors caused by quantization (which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}. 
\end{equation}
%
%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
Notice that, due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (indeed, all other errors described in this paper are ensured to
fulfil this property in our implementation). 
We also remark that, due to its native digital implementation, 
there are no parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the controller. 
Thus $\hat{C}(z) \equiv C(z)$.

@@

A typical digital control system with a continuous plant and a discrete
controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
ADC converters introduce quantization errors (notice that each of them
may have a different FWL representation than the controller),
which are modeled as disturbances 
$\nu_{1}(z)$ and $\nu_{2}(z)$;  
$G(s)$ is the continuous-time plant model
with parametric additive uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$ (as mentioned above);  
$R(z)$ is a given reference signal; 
$U(z)$ is the control signal; 
and $\hat{Y}(z)$ is the output signal affected by the disturbances and uncertainties in the closed-loop system 
%
%
%
The ADC and DAC may be abstracted by transforming the closed-loop system in
Figure~\ref{fig:sampledsystem} into the digital system in 
Figure~\ref{fig:digsystem1}, 
where 
% the parametric uncertainties are represented by~$\Delta_p \vec{G}$ and 
the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
seen as additive noise.

@@

In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
parametric uncertainties related to modeling errors  
(which are represented by~$\Delta_p \vec{G}$),  
and uncertainties introduced by quantizations in the ADC and
DAC conversions ($\nu_1$ and $\nu_2$) which are assumed to be non-deterministic. 
Recall that we discussed how the quantization noise is encompassed as an additive term, 
which means it does not enter parametrically in the transfer function. 
Instead, we later show that the system is stable given these non-deterministic disturbance inputs.

@@

Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
and of quantization disturbances in the closed-loop system.  
Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
and $Q2$ (DAC) be the source of a white noise $\nu_{2}$.  The following equation
models the system in Figure~\ref{fig:sampledsystem}, encompassing the
parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
the controller $\hat{C}(z)$:
%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)C(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\hat{C}(z)\hat{Y}(z). 
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\nu_{2}(z)+H_{3}(z) R(z),
\end{equation}
%
where
%
\begin{equation*}
H_{1}(z)=\frac{1}{1+\hat{G}(z) \hat{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z) \hat{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{3}(z)=\frac{\hat{G}(z) \hat{C}(z)}{1+\hat{G}(z) \hat{C}(z)}. 
\end{equation*}

@@

A discrete-time dynamical system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if bounded inputs necessarily result in bounded outputs. 
This condition holds true over an LTI model if and only if every pole of its transfer function lies inside the unit circle \cite{Astrom08}.  
Analyzing Eq.~\eqref{eq:outputfunctions}, 
the following proposition provides conditions for the BIBO stability of the system in Figure~\ref{fig:sampledsystem}, 
with regards to the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded 
(in particular, the bound on the quantization noise is given by
Assumption~\ref{whitenoise}). 
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and uncertain discrete
model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
\end{equation}
\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
\red{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply! correct?}
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  
Assuming a precision of $I_p=16$, $F_p=24$,  
\blue{[so you mean we're not using Jury's criterion? pllease clarify.] the digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
}
We start with an a-priori candidate solution with all coefficients zero: 
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ 
\tilde{C}(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$
\blue{[here recall that indeed this C equates to the tilde version, because \ldots ]}
In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\tilde{C}(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
\tilde{C}(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

Figure~\ref{fig:step} illustrates the step responses of the closed-loop
system with the original controller represented by
Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), the
first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate
solutions provided by \tool.  The step response in Figure~\ref{fig:step0}
confirms the stability loss if we consider FWL effects.  
Figure~\ref{fig:step1} shows that the first candidate controller is able to
stabilize the closed-loop system without uncertainties, but it is rejected
during the {\sc precision} phase by \tool since this solution is not
considered to be sound.  Finally, Figure~\ref{fig:step2} shows a stable
behavior for the final (sound) solution, which presents a lower settling
time (hence the noticeable digitazion effect).

@@

The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time.  
\blue{[great, all good: how much uncertainty have you introduced? where precisely? in the coefficients or as an exogenous disturbance? ]}
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
CBMC (SHA-1 hash) version: \\ 
7a6cec1dd0eb8843559591105235f1f2c4678801}
